Proportional multi-state multiple-cohort life table model

### 2018-04-19 MSLT/MSLTdoc.Rmd
Graphs aes

##Do graph with another layer for original rates in age groups for comparison purposes.
p <- ggplot() +
            geom_line (
              data = interpolated,
              mapping = aes(ages,rate) 
              ) +
              geom_point(
                data = data, 
                mapping = aes(age_cat, one_rate)
                ) +
           theme_classic()
           print(p)
  }
}

>>>>

##Do graph with another layer for original rates in age groups for comparison purposes.
p <- ggplot(data = interpolated,mapping = aes(ages,rate)) +
              geom_line(aes(color = "Interpolated")) +
              geom_point(
                data = data, 
                mapping = aes(age_cat, one_rate, color = "Original")) +
              labs(colour="",x="Age",y= paste(i_sex, i_measure, "rates", sep = " "))+
            labs (title = paste("Rates", i_sex, i_measure, sep = " "), size=14) +
            theme_classic() +
            theme(plot.title = element_text(hjust = 0.5))
           print(p)
  }
}
